gij bent 2

### 2024-12-18 paper/paper.qmd
typo correction and years cclamp added

[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from XXX to XXX. The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.

@@

Another aspect of of the complex-adaptive system of language are the connections between people. Humans are embedded in larger social networks, which are formed according to a so-called "power law". This means the network has a small number of people with a large number of connections, supplemented by many people who have relatively few connections [@barabasi_emergence_1999].

>>>>

[^c-clamp]: More recently, the release of the C-Clamp corpus [todo] offers a diachronic insight into the language use of Dutch-speaking writers from 1837 to 1999. The historical nature of this corpus, however, limits its use for research into contemporary language variation phenomena.

@@

Another aspect of the complex-adaptive system of language are the connections between people. Humans are embedded in larger social networks, which are formed according to a so-called "power law". This means the network has a small number of people with a large number of connections, supplemented by many people who have relatively few connections [@barabasi_emergence_1999].
